---
title: "gganimatePractice"
author: "Jeff Grayum"
date: "11/21/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading libraries.
```{r}
library(tidyverse)
library(gganimate)
library(gapminder)
library(ggthemes)
#install.packages("gifski")
library(gifski)
```

Making base graph of gdpPerCap vs lifeExp
```{r}
gapminder%>%
  ggplot(aes(gdpPercap, lifeExp, color = continent, size = pop)) +
  geom_point() +
  labs(x = "GDP per capita",
       y = "Life Expectancy",
       color = "Continent",
       size = "Population",
       title = "Comparing life expectancy with a countries GDP per capita")
```

Make that basic graph look beautiful.
```{r}
gapminder%>%
  ggplot(aes(gdpPercap, lifeExp, color = continent, size = pop)) +
  geom_point(alpha = 0.7, stroke = 0) +
  theme_fivethirtyeight() +
  scale_size(range = c(2, 12), guide = "none") +
  labs(x = "Income per person (GDP/capita)",
       y = "Life Expectancy",
       color = "Continent",
       size = "Population",
       title = "Comparing life expectancy with a countries GDP per capita",
       caption = "Source: Gapminder") +
  theme(axis.title = element_text(),
        text = element_text(family = "Times New Roman"),
        legend.text = element_text(size = 10)) +
  scale_color_brewer(palette = "Set2")
```


Now, lets use gganimate to make a dynamic graph that shows how these trends change over time.
```{r}
graph1animation <- graph1 +
  transition_time(year) +
  labs(subtitle = "Year: {frame_time}") +
  shadow_wake(wake_length = 0.1) #this will leave a "trail" of 10% (.1) of the frames

graph1animation 
```


Let's continue to improve our animation, and customize it.
```{r}
animate(graph1animation, height = 500, width = 800, fps = 50, duration = 10,
        end_pause = 100, res = 100)
```

Now, save your graph.
```{r}
anim_save("gapminder_graph_GDPperCapVSlifeExp.gif")
```


Graph 2. Data gradually appearing over time.
```{r}
#per his example:  genre = continent, year = year, gdpPerCap = sales.
#First, summarized your data!

gapminder2 <- gapminder %>%
  group_by(continent, year) %>%
  summarize(meanGdp = mean(gdpPercap)) %>%
  view()


gapminder2 %>% 
  ggplot(aes(year, meanGdp, color = continent)) + 
  geom_line()
```


Now, for fun, we will make our graph pretty. SWEET DARKMODE GRAPH!!
```{r}

graph2 <- gapminder2 %>% 
  ggplot(aes(year, meanGdp, color = continent)) + 
  geom_line(size = 1.1) +
  theme_solarized_2(light = FALSE) +
  labs(title = "GDP per capita over time, grouped by continent",
       subtitle = "From 1952 - 2007",
       x = "",
       y = "Income per person (GDP per capita)",
       color = "Continent",
       caption = "Source: Gapminder") +
  theme(axis.title = element_text(),
        text = element_text(family = "Times New Roman"),
        legend.text = element_text(size = 10)) +
  scale_color_brewer(palette = "Set2") + #NOTE also can set palette to "Pastel1:3"
  geom_point() + #Adds a point to your animation, at the end of the line.
  scale_x_continuous()

```


Animate it!  Instead of calling transition_time(), we will call transition_reveal().
I don't really like this style of animation. :( Doesn't add much info.
```{r}
graph2.animate <- graph2 +
  transition_reveal(year)
```


It's a dumb animation, but let's make it beautiful.
```{r}
graph2.animate <- graph2 +
  transition_reveal(year) +
  view_follow(fixed_y = TRUE) #this sets our y axis, but x axis will expand with time. It's dumb.
```

Further improvement, and saving the animation.

```{r}
animate(graph2.animate, height = 500, width = 800, fps = 50, duration = 10,
        end_pause = 100, res = 100)

anim_save("gapminder_graph_GDPperCapVStime.gif")
```

The final animated graph will TRANSITION BETWEEN STATES!
```{r}
#First, download the csv file from Kraggle.  Move it into the project director, set working directory to "Project Directory", and then read_csv().  IDK if this is the ideal way to accomplish this, but it worked.

reviews <- read_csv("googleplaystore.csv") %>%
  filter(Category %in% c("GAME", "SOCIAL", "PRODUCTIVITY", "TOOLS", "EDUCATION"))

#Now make a basic boxplot, showing average ratings per category.
graph3 <- reviews %>%
  ggplot(aes(Category, Rating, fill = Category)) +
  geom_boxplot() 

```

Now let's make that boxplot beautiful.
```{r}
graph3 <- reviews %>%
  ggplot(aes(Category, Rating, fill = Category)) +
  geom_boxplot() +
  theme_fivethirtyeight() +
  labs(title = "Google Play Store ratings",
       x = "Category",
       y = "Average rating",
       fill = "Category",
       subtitle = "Source: Kraggle.com") +
  theme(legend.position = "none",
        axis.title.y = element_text(),
        text = element_text(family = "Times New Roman"),
        panel.grid.major.x = element_blank(),
        axis.title.x = element_blank()) +
  scale_fill_tableau() #nice color palette. 
```


Now, we will animate!
```{r}
graph3.animation <- graph3 +
  transition_states(Category, wrap = FALSE) +
  shadow_mark(alpha = 0.5) +
  enter_grow() + #Each plot will "grow"
  exit_fade() + #Plots will fade to alpha = 0.5 when new ones appear
  ease_aes("back-out")

anim_save("googlePlayRatingsBoxplot.gif")
``` 

